\begin{center}
    \textbf{\underline{\uppercase{ACKNOWLEDGEMENT}}}
\end{center}

I am sincerely thankful for my family and friends who have
accompanied me throughout my undergraduate years. This
thesis would not have happened without your help.

To Dr Denis, I would not have completed this thesis
without your advice and support. Thank you for your
unreserved feedback and comments which materialised this thesis
and pushed me beyond what I thought I could achieve alone.

To my mother who has been taking care me,
thank you for ensuring that I
am well-fed and for putting a roof over my head. Your
unconditional love and support have enabled me to focus on
writing my thesis.
现在是我慈乌反哺以感谢您养育之恩的时候.

To my beloved half - Peiyi, thank you for sharing my worries
and helping to proofread my thesis. Without you, writing
this thesis would be another A-level GP challenge for me.
Thank you for showering me with love and welfare when I was
too busy to take care of myself. I really appreciate
everything you have done for me and I look forward to
disturbing you for a lifetime.

To my friends, thank you for all the fun times we had in
university. Although half of our university years were spent
at home, I still consider us the lucky batch as we managed
to have fun during our freshmen year and created wonderful
memories together in hall. I was also fortunate enough to
experience student exchange in Boston with some of you
before all the lockdowns happened, and it was really an
eye-opening experience to study abroad. 
Not to forget our weekly study group, thank you for all the
bubble tea and snacks, really boosted my grades and weight.
My university life
would not be the same without you all, and I really
appreciate the friendships we forged.

Lastly, to juniors who are considering if you should write a
thesis, I would encourage you to do so. It is definitely not
an easy journey, but I believe the sense of accomplishment
and the research know-how you learned from this process will
be a useful experience for your future endeavors. All the
best!

May God be with us all.
