<!-- # Model -->

This chapter focuses on explaining the model architecture
used in this paper. An overview is provided here before deep
diving into specific concepts at the sub-chapters.

The fundamental idea of our model is based on no arbitrage
asset pricing model, which assumes a stochastic discount
factor such that there is no expected excess return,
and no arbitrage opportunity available. We implement
the no arbitrage condition as our loss function.
The backbone of our model is a Generative Adversarial
Network Model (GAN) which consist of two competing
feed forward neutral network called discriminator and
generator. The discriminator models the non-linear
relationship between factors and stochastic discount factor.
The generator models the non-linear relationship between
factors and mis-pricing, a latent variable that violates the
no-arbitrage pricing assumption.
We include a long short-term memory (LSTM) network to
extract macroeconomic factors into the discriminator and
generator. Discriminator and generator have different LSTM
network to handle for the possibility of different
information set is required for different networks.
We use Fama-French factor model as the baseline comparison. 
Fama-French factor model models stochastic discount factor
as a linear combination as selected factors. The underlying
model is a linear regression.

```{r, child=("model/neural_network.Rmd")}
```

```{r, child=("model/lstm.Rmd")}
```

```{r, child=("model/no_arbitrage.Rmd")}
```

```{r, child=("model/gan.Rmd")}
```

```{r, child=("model/fama_french.Rmd")}
```
