<!-- # Model -->

This chapter focuses on explaining the empirical approach used in this
paper. First, we present the no-arbitrage asset-pricing
model that is the foundation of our base model: the
Fama-French factor model and the GAN model. Next, we
expand the no-arbitrage condition to construct a pricing
loss function used in the GAN model. Then, we describe a
simple feed-forward neural network before exploring a
recurrent neural network model that considers data dynamics.
Following that, we explain the GAN model, which
consists of two neural network models competing based on the
pricing loss function and end the chapter
with an explanation for the Fama-French factor model.

Training neural network models is an empirical challenge.
Regularization techniques are commonly used in machine
learning to prevent over-fitting and improve model training
results. @chen_deep_2021 adopted a dropout strategy proposed
by @srivastava_dropout_2014.
This paper further includes early stopping rules introduced
by @yao_early_2007.
The discussion on neural networks presented in this section
is referenced from the
Hands-On Machine Learning with Scikit-Learn and TensorFlow
by @geron_hands-machine_2017.

```{r, child=("model/no_arbitrage.Rmd")}
```

```{r, child=("model/neural_network.Rmd")}
```

```{r, child=("model/lstm.Rmd")}
```

```{r, child=("model/gan.Rmd")}
```

```{r, child=("model/fama_french.Rmd")}
```

