<!-- # Empirical findings -->

The [Data](#data) section describes two types of
datasets: *factor* and *fundamental* data.
The *factor data* training contains more assets but lesser
characteristic data, while *fundamental data* training
contains more characteristic data with lesser assets.
Therefore, readers should consider the difference across the
datasets used when interpreting the results.
<!--
This paper proposed interpreting the difference in results
as a trade off between flexible GAN model
against a simple linear factor model under different number
of covariates and assets.
-->
Generally, neural network models require a large dataset for
training. However, as @noauthor_google_2019 recommended in their
developer website, there is no common consensus among
literature and the required size of dataset may be
context-dependent.

```{r, child=("./results/sharpe.Rmd")}
```

<!--
## Mispricing error

As explained in [Mispricing error with beta
representation](#beta), the assets' expected excess return
relates to the SDF in a one-factor model with $\alpha_i =
0$. As the mispricing error is asset dependent, this paper
first presents summary statistics on the individual asset
before presenting on characteristic sorted portfolios
created by @gregory_constructing_2011.

```{r, child=("./results/mispricing_error_individual.Rmd")}
```

```{r, child=("./results/mispricing_error_portfolio.Rmd")}
```
-->
