<!-- # Empirical findings -->

As described in the chapter on [data](#data) description,
this paper splits the dataset into *factor* and *fundamental*
data due to the limited training available.
The *factor data* training contains more assets but lesser
characteristic data, while *fundamental data* training
contains more characteristic data with lesser assets.
When interpreting the results, the reader should consider
the difference in the dataset used.
This paper proposed interpreting the different in results
between datasets and models as a realistic trade off between
selecting a flexible GAN model and a simple linear factor
model when faced with a different number of covariates and
assets.

```{r, child=("./results/sharpe.Rmd")}
```

<!--
## Mispricing error

As explained in [Mispricing error with beta
representation](#beta), the assets' expected excess return
relates to the SDF in a one-factor model with $\alpha_i =
0$. As the mispricing error is asset dependent, this paper
first presents summary statistics on the individual asset
before presenting on characteristic sorted portfolios
created by @gregory_constructing_2011.

```{r, child=("./results/mispricing_error_individual.Rmd")}
```

```{r, child=("./results/mispricing_error_portfolio.Rmd")}
```
-->
