---
output:
    bookdown::pdf_document2:
        template: ./template/thesis_template.tex
        fig_caption: yes
        keep_tex: yes
        number_sections: yes
        toc: true
        toc_depth: 2
        latex_engine: xelatex
title: "Generative Adversarial Network (GAN) model in Asset Pricing"
author: "Wang Lingjie"
keywords:
    "
    Generative Adversarial Network, Asset Pricing,
    Stochastic Discount Factor, Machine Learning,
    Deep Learning, Stock Returns
    "
bibliography: ref.bib
csl: ./template/apa.csl
nocite: ""
abstract: 
    "
    An important topic in asset pricing is explaining
    the variation in expected returns of financial assets.
    No-arbitrage pricing theory suggests the idea of a
    pricing kernel that governs asset prices.
    However, it remains a challenge to estimate the
    asset-pricing kernel. The difficulties include (1)
    choosing the right factors, (2) estimating the pricing
    kernel’s functional form, and (3) selecting the right
    portfolio to estimate the kernel.
    Recently, @chen_deep_2021 proposed a Generative
    Adversarial Network (GAN) model that attempts to solve
    all three challenges in a single setup and claim to
    achieve the best performance compared to all existing
    models.
    This paper seeks to empirically validate @chen_deep_2021's
    research based on the United States stock data
    with the United Kingdom (UK) London Stock Exchange 
    1998 - 2017 data.
    This paper found that the GAN model outperformed
    the benchmark four-factor model in terms of Sharpe ratio.
    "
acknowledgement: "acknowledgement.tex"
---

```{r echo=F, warning=F, message=F}
# libraries
library(tidyverse)
library(kableExtra)
```

<!-- introduction -->
# Introduction
\thispagestyle{plain}

```{r, child=("introduction.Rmd")}
```

<!-- literature review -->
# Literature Review
\thispagestyle{plain}

```{r, child=("lit_review.Rmd")}
```

<!-- model -->
# Methodology
\thispagestyle{plain}

```{r, child=("model.Rmd")}
```

<!-- model training -->
# Model Training {#model_training}
\thispagestyle{plain}

```{r, child=("training.Rmd")}
```

<!-- model evaluation -->
# Evaluation metrics
\thispagestyle{plain}

```{r, child=("metrics.Rmd")}
```

<!-- data -->
# Data {#data}
\thispagestyle{plain}

```{r, child=("results/data.Rmd")}
```

<!-- empirical results -->
# Empirical findings
\thispagestyle{plain}

```{r, child=("results.Rmd")}
```

\newpage

# Discussion
\thispagestyle{plain}

```{r, child=("discussion.Rmd")}
```

<!-- conclusion -->
# Conclusion
\thispagestyle{plain}

```{r, child=("conclusion.Rmd")}
```

<!-- references -->
\newpage

# Bibliography
\thispagestyle{plain}
