---
title: "Generative Adversarial Network (GAN) model in Asset Pricing"
author: "Wang Lingjie"
output: 
    beamer_presentation:
        theme: "Boadilla"
        toc: false
        keep_tex: true
header-includes:
    - \AtBeginDocument{\title[GAN model in Asset
        Pricing]{Generative Adversarial Network (GAN) model
        in Asset Pricing}}
bibliography: ../ref.bib
csl: ../template/apa.csl
---

# Overview

- Motivation
- Literature review
- Research objective
- Methodology
- Evaluation metrics
- Data
- Results
- Discussion
- Conclusion

# Motivation

```{r child=("motivation.Rmd")}
```

# Literature review

```{r child=("literature.Rmd")}
```

# Research objective

```{r child=("intro.Rmd")}
```

# Methodology

```{r child=("method.Rmd")}
```

# Evaluation metrics

```{r child=("metric.Rmd")}
```

# Data

```{r child=("data.Rmd")}
```

# Results

```{r child=("results.Rmd")}
```

# Discussion

```{r child=("discussion.Rmd")}
```

# Conclusion

```{r child=("conclusion.Rmd")}
```

# Questions

\begin{center}
    \Huge Thank you
\end{center}

# Annex

\begin{center}
    \Huge Annex
\end{center}

```{r child="annex.Rmd"}
```

# References {.unlisted .unnumbered .allowframebreaks}
